### 2021-02-16 tarea_base_enigh/01-script.Rmd
Update 01-script.Rmd

#______________________________________________________________________________
#______________________________________________________________________________
#DATA wranwilng para STATA (version A)
data<-original%>% 
  select(folioviv,foliohog,est_socio,alimentos,leche,huevo)%>%
  mutate(p_leche=18.72,s_leche=leche/alimentos, q_leche=leche/18.72,
         p_huevo=28.5,q_huevos=huevo/28.5,s_huevo=huevo/alimentos,
         q_other=30,s_other=(alimentos-leche-huevo)/alimentos, p_other=30/s_other)

>>>>

#______________________________________________________________________________
#______________________________________________________________________________
#DATA wrangling para STATA (version A)
data<-original%>% 
  select(folioviv,foliohog,est_socio,alimentos,leche,huevo)%>%
  mutate(p_leche=18.72,s_leche=leche/alimentos, q_leche=leche/18.72,
         p_huevo=28.5,q_huevos=huevo/28.5,s_huevo=huevo/alimentos,
         p_other=30,other=(alimentos-leche-huevo),s_other=other/alimentos, q_other=other/30)
